### 2015-01-18 src/tbl.subsumption.Rnw
remove ellipse

\begin{table*}[!ht]
<<tblsubsumption,results='asis'>>=
library(ellipse)
print(xtable(1 - subsumption.db, caption='subsumption', label='table:subsumption'), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
@
\caption{The subsumption relationship.}
\end{table*}

>>>>

\begin{table*}[!ht]
<<tblsubsumption,results='asis'>>=
print(xtable(1 - subsumption.db, caption='subsumption', label='table:subsumption'), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
@
\caption{The subsumption relationship.}
\end{table*}
